---
title: "W_UP_01"
author: "Jessica Villa"
date: "Summer 2022"
output: html_document
---



The report structure should include five sections.  see below



```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
mydata <- read.csv(file="pushups.csv")
```

# Introduction

<!--In this section you explain what you are trying to show. Where did the data come from? What is the research or other question you are trying to answer?!-->

Create an Rstudio project in your shared space on rstudio.cloud.  Using the dataset called pushups from the tigerstats package in R; answer the question posed by this null and alternate hypothesis in an html markdown document.

$H_0$: There is no difference between the average number of pushups of line vs skill players

$H_A$: The average number of pushups done by line players is statistically different than that of skill players.

# Methods

<!--Decide on your methods: use "variable analysis" or other appropriate descriptors. Make sure to choose at least one graphical method and at least one numerical method.!-->
Position are a categorical variable. Push ups is a numerical variable. I will do an analysis that explains push ups based on positions. 
# Results

<!--Divide this section into two sub-sections: One for your descriptive results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results
```{r}
boxplot(pushups~position,data=mydata)
```

This is push-ups on the y-axis of the box plot. While there is positions on the x-axis. On the box plot, there is a large segment on each whisker plot. The average push ups for the position appears to be different. The skill position appears to do more push-ups based of of the y-axis (pushups)
<!--Graphical results here. Make sure to show your code. Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too. Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->

### Numerical Descriptive Results
```{r}
favstats(pushups~position,data=mydata)
```
The median for both positions is way different. It appears the median for the skill position is much higher. It's higher by 33. The maximum amount of push-ups someone could do in the line position was 34. While in the skill position, it was 108 push-ups. A difference of 74 push-ups. So far, it looks like the skill position is far more capable of completing the mosy push-ups. To further my point, the mean for the skill position was roughly 33 more push-ups.

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

## Inferential Results
```{r}
t.test(pushups~position,data=mydata)
```
Our p-value is 0.000009421. Our df value is 27.079. Our t value is -5.4341. Our alternative hypothesis ia shown. It states 'true differences in means between group LINE and group skills is not equal to 0. Our sample estimates are: mean in group LINE is 17.12500; mean in group SKILL is 49.72 If our null hypothesis is true,  the p value is the probability of getting our results. LINE vs SKILL. It is very rare. The p-value is so small we reject (ignore) the null hypothesis. If it's greater than .05, you failed to reject the null hypothesis (that's bad). If i reject the null hypothesis, I am 95% sure the SKILL group can do more push-ups. 
<!--State hypothesis clearly. Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc. Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->



# Discussion and Conclusion         


<!--Discussion and conclusion here. If you found a relationship be sure to consider whether the relationship occurs because one of the variables causes the other, or whether they perhasps are related for some other reason. Watch the chapter 6 videos from the GeorgeTown videos collection.!-->

The original question was this: 'Who could do the most push-ups? The SKILL position or the LINE position under a specific amount of time? 'Our response: based off of our numerical descriptive results and our inferential results; we can see the SKILL position can do MORE push-ups than the LINE position under any amount of time given. We used a boxplot and a table to figure out our values and percentages. 